\section{Models}
\input{szmodels}

\subsection{Problems with the GNFW model}
\label{sec:ss}
\input{gnfwproblems}

\subsection{Other Models}

\subsubsection{Image Model}

Generic images can also be used in \climax\ as models, via
\code{adddataset} with \code{type = image}.  Supported image types,
and manipulation are as described in \S\ref{sec:imagehandling}.

Image models support only the components common to all 2D models:
translation (offsets), rotation, and scaling (normalization).  When
reading in images, you must specify either a background level, or
provide a region of the image from which it can be estimated.  This
allows for real data images to be used as models, for which a
background (i.e., constant offset) would significantly skew any
goodness-of-fit estimator.  

On read-in, this background will be subtracted from the image, and the
resulting image normalized to unity at the peak.  When comparing image
models to radio or xray data, the usual requirements for specifying
the appropriate normalization apply (i.e., \code{Sradio} or
\code{Sxray} in appropriate units).  Note that no assumptions are made
about the source of the image data; for example, if the source is an
xray surface brightness image, for example, you will probably want to
apply an appropriate transformation (i.e., \code{trans = sqrt}) to the image
before using it as an SZ model.

Currently, two operations are supported for evaluating an image model
at a requested offset, by using the \code{oper} keyword: returning the
value of the nearest pixel (\code{oper = nearest}), or interpolating
at the requested point (\code{oper = interpolate}).  For offsets that
lie outside of a model image, a zero value is returned, and the pixel
is marked as invalid.  

Invalid pixels will not be used in evaluating the likelihood for
image-plane models, however note that Fourier-plane datasets cannot
exclude individual pixels, and the zero values will be incorporated
into the transform and hence the likelihood evaluation.  You should
think carefully about what makes sense for your use-case.  Supplying a
valid image that is large enough to accomodate any offset explored by
the Markov chain can eliminate this potential problem.

An example of using an \xray-derived image model to fit SZ data is included below:

\begin{myindentpar}{3cm}
\small
\begin{verbatim}
adddataset name=sz type=uvf;
sz.file=A1914.uvf;
sz.uvmax = 2000;
sz.display = true;

addmodel name=im type=image;
im.file=acisf00542N004_cntr_img2.fits;
im.npix = 64;
im.thetaMinErr = 0.04 deg;
im.display = true;
im.interactive = true;
im.trans = sqrt;
im.sigmasmooth = 20";

im.Sradio = -2000:0 muK;
im.xoff = -0.01:0.01 deg;
im.yoff = -0.01:0.01 deg;
im.rotang = -90:90 deg;

nburn = 3000;
ntry  = 10000;

\end{verbatim}
\end{myindentpar}
